---
title: "BBH-SST"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This projects demonstrates one simple organizational path using Maine Department of Marine Resources' [Boothbay Harbor SST Time Series](https://www.maine.gov/dmr/science/weather-tides/boothbay-harbor-environmental-data).

## Getting ready

### Got packages?

If you don't have the required R packages you'll need to install each.  You need only need to do this once, but if you upgrade R you may need or want to update these, too.

```{r}
required_packages <- c("dplyr", "readr", "ggplot2", "jsonlite", "fs", "here")
current_packages <- rownames(installed.packages())
for (package in required_packages){
  if (!(package %in% current_packages)) install.packages(package)
}
```

### Load packages and functions

For the purposes of just this `README` we'll load the [fs](https://CRAN.R-project.org/package=fs) package.

Otherwise, all we need to do is source the `setup.R` file.

```{r}
library(fs)        # this is just for use in this README
source("setup.R")  # this is the good stuff
```

This small project organizes data, images, literature and code into subdirectories. It's pretty self-explanatory, but do take a look at `setup.R` to see what is going on.

```{r}
fs::dir_tree()
```

If you study `setup.R` you can see that we created three directory paths in the global environment.  You access these just like you had defined them manually.

```{r}
list.files(CODEPATH)
```

### Read the data

We created input-output functions, that `setup.R` sourced so they are now in your global environment.

```{r}
x <- read_bbh()
dplyr::glimpse(x)
```

### Plot the data

`setup.R` also sourced a function for plotting the data.

```{r}
plot_bbh(x)
```

We can modify the range of time - in essence zooming into recent times. Let's filter out just the records from Jan 1 2016 through today.

```{r}
x |>
  dplyr::filter(dplyr::between(date, as.Date("2016-01-01"), Sys.Date())) |>
  plot_bbh()
```

Because `plot_bbh()` returns a plot object we can add another layer - perhaps a smoothing line would be nice?

```{r, message = FALSE, warning = FALSE}
x |>
  dplyr::filter(dplyr::between(date, as.Date("2016-01-01"), Sys.Date())) |>
  plot_bbh() +
  ggplot2::geom_smooth(level = 0.99)
```